Untitled

### 2022-04-27 Supplementary_Material/Sup_Mat_Lanuza_et_al_2021_Ecology_Letters.Rmd
minor edit on supp mat

- Nectar provision: We recorded the presence and absence of nectar for all species. In addition, we also searched for microlitres and milligrams of nectar per flower and nectar concentration. For species that did not have nectar information but belonged to a family that is considered as ‘nectarless’, this trait was recorded at family level and the species was recorded with ‘absence’ of nectar. This was done exclusively for well documented nectarless taxonomical groups. For the field of microlitres of nectar, we considered single measurements of nectar standing crop. In general terms, the timming of the measurement and methodology differed across studies. For instance, some studies measured nectar in freshly opened flowers while others in flowers that were bagged for 24 hours. Despite the different methodologies to measure nectar provision, we believe that this is an interesting field that allows the macroecological exploration of this important floral reward in relation with the rest of reproductive traits at a global scale.

>>>>

- Nectar provision: We recorded the presence and absence of nectar for all species. In addition, we also searched for microlitres and milligrams of nectar per flower and nectar concentration. For species that did not have nectar information but belonged to a family that is considered as ‘nectarless’, this trait was recorded at family level and the species was recorded with ‘absence’ of nectar. This was done exclusively for well documented nectarless taxonomical groups. For the field of microlitres of nectar, we considered single measurements of nectar standing crop. In general terms, the timming of the measurement and methodology differed across studies. For instance, some studies measured nectar in freshly opened flowers while others in flowers that were bagged for 24 hours. Despite the different methodologies to measure nectar provision, we believe that this is an appropriate way to collate measurements of nectar to explore trait associations at a macroecological scale.
